Capturing Subdiffusive Solute Dynamics and Predicting Selectivity in Nanoscale Pores with Time Series Modeling

### 2020-04-28 Ben_Manuscripts/stochastic_transport/cover_letter_JCTC.tex
JCTC cover letter, emphasizing methods.

	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia and Michael R.
	Shirts, for consideration for publication as an Article in the Journal of 
	Physical Chemistry B. We expect this work to be of significant interest to 
	researchers who study complex transport in both structured and amorphous 
	soft materials. Please note that this article has been uploaded to arXiv with
	differences only in formatting: \href{https://arxiv.org/abs/2004.07905}{https://arxiv.org/abs/2004.07905}. \\

	In this article, we use solute trajectories generated from 5$\mu$s molecular
	dynamics (MD) simulations of an inverted hexagonal (H\textsubscript{II}) phase
	self-assembled lyotropic liquid crystal (LLC) polymer membrane in order to 
	parameterize two different stochastic time series models capable of predicting
	solute flux and selectivity on a macroscopic scale. Realizations of both models
	quantitatively reproduce the mean squared displacements (MSDs) exhibited by 
	solutes in MD simulations. This is among the first studies to apply time 
	series modeling of molecular simulations in order to predict bulk materials properties.\\

	This article builds on recent work of ours also published in J. Phys. Chem. B 
    where we characterized transport mechanisms exhibited by a series of 
	small polar solutes in an LLC Membrane (Coscia and Shirts \textit{J. Phys.
	Chem. B}, 123, 6314--6330 (2019)). In that study, we observed subdiffusive solute transport
	characterized by intermittent hops separated by periods of entrapment. In
	this work, we build on the chemical intuition gained from our previous study
	in order to formulate stochastic models which produce trajectory realizations
	that share the same dynamical properties as those exhibited by solutes in 
	our MD simulations. We explore two modeling approaches. First, based on the
	anomalous diffusion literature, we parameterize solute motion as 
    subordinated fractional Brownian and L\'evy motion processes, based on the observation that 
	solutes experience a series of dwell times separated by anti-correlated hop
	lengths. Our second approach adds state-dependent dynamics to standard Markov
	state modeling approaches. We model solute motion as a series of transitions
	between various trapped states, each with different dynamical properties.
	Finally, we demonstrate how one can project our best model onto macroscopic 
	timescales in order to estimate solute flux and selectivity.\\

>>>>

	We are submitting ``\ManuscriptTitle'' by Benjamin J. Coscia
        and Michael R.  Shirts, for consideration for publication as
        an Article in the Journal of Chemical Theory and
        Computation. We expect this work to be of significant interest
        to researchers who study complex transport at the molecular
        level by adding important new techniques for estimating long
        time scale behavior, inferring mechanisms, and estimating bulk
        transport behavior from molecular trajectories. Please note that this article has been uploaded to arXiv with
	differences only in formatting: \href{https://arxiv.org/abs/2004.07905}{https://arxiv.org/abs/2004.07905}. \\

	In this article, we analyze solute trajectories generated from
        5$\mu$s molecular dynamics (MD) simulations of an inverted
        hexagonal (H\textsubscript{II}) phase self-assembled lyotropic
        liquid crystal (LLC) polymer membrane to parameterize two
        different stochastic time series approaches capable of
        predicting solute flux and selectivity on a macroscopic
        scale. Both approaches quantitatively reproduce the mean
        squared displacements (MSDs) exhibited by solutes in MD
        simulations. This is among the first studies to apply time
        series modeling of molecular simulations in order to infer
        mechanisms, propagate behavior to long time scaless and,
        estimate bulk materials properties.\\

	This article builds on recent work of ours published in
        J. Phys. Chem. B where we characterized transport mechanisms
        exhibited by a series of small polar solutes in an LLC
        Membrane (Coscia and Shirts \textit{J. Phys.  Chem. B}, 123,
        6314--6330 (2019)). In this work, we build on the chemical
        intuition gained from our previous study in order to formulate
        stochastic models which produce trajectory realizations that
        share the same dynamical properties as those exhibited by
        solutes in our MD simulations. We explore two main modeling
        approaches. First, using anomalous diffusion theory, we
        parameterize solute motion as subordinated fractional Brownian
        and L\'evy motion processes, based on the observation that
        solutes experience a series of dwell times separated by
        anti-correlated hop lengths. Secondly, we add state-dependent
        dynamics to standard Markov state modeling approaches, where
        we model solute motion as a series of transitions between
        various trapped states, each with different dynamical
        properties.  Finally, we demonstrate how one can project our
        best model onto macroscopic timescales in order to estimate
        solute flux and selectivity.\\
